\thesistitle

### 2019-07-18 sections/clonerefactor.tex
Fixed equations

In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of n_1 and n_2) and the fragment on the right (consisting of n_3 and n_4) are two clone instances of a clone class. Table \ref{table:equalityarrays} shows their corresponding equality arrays.

@@

\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
\end{equation}

>>>>

In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of $n_1$ and $n_2$) and the fragment on the right (consisting of $n_3$ and $n_4$) are two clone instances of a clone class. Table \ref{table:equalityarrays} shows their corresponding equality arrays.

@@

\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1) \exists (y \in E_2) x<0 \lor y<0 \Rightarrow x=y
\end{equation}
